Evaluating infectious disease forecasts with allocation scoring rules

### 2023-12-12 alloscore_manuscript/alloscore-application.Rnw
adding complete multi-k section draft to manuscript.

The integrated allocation score summarizes allocation scores across a range of possible values of the constraint ($K$), possibly taking weights into account for different values of $K$ that might be more or less likely (Section \ref{sec:methods.detailed.integrated_allocation}).
This could be useful in situations where the actual constraint may not be known, or could only be specified as a probability distribution.
Unlike in the above analyses where we conducted analyses assuming that $K$ was known to be 15,000, the analyses in this subsection are conducted assuming different distributions of $K$.

@@

Allocation scores (AS) were computed for a range of $K$ from 200 to 60,000 for forecasts made on 2020-12-20 predicting levels of hospitalizations on 2021-01-03 (Figure \ref{fig:multi-k}A).
These calculations highlight that allocation scores were highest at the $K$ nearest to the observed value of \Sexpr{format(tot_y, big.mark = ",")}.
Rankings of allocation scores from all models were fairly stable across a range of values for K, with some crossings, especially at $K$ values further away from the observed value.

Integrated allocation scores (IAS) were computed for two distributions of $K$, one uniform across the entire range and the other a symmetric distribution around 15,000 (Figure \ref{fig:multi-k}B).
Both versions of the IAS were correlated with the original AS conducted at $K=15,000$, with the higher correlation coming from the distribution that was centered at $K=15,000$ (Figure \ref{fig:multi-k}C).

Interpretation of Figure \ref{fig:multi-k} needed.

@@

<<multi-k-scores, results='asis'>>=
left_join(ias, as) |>
  rename(`IAS centered at 15k` = IAS_wt,
         `IAS uniform` = IAS) |>
  xtable::xtable(caption = "Allocation scores shown in Figure \\ref{fig:multi-k}C, sorted by Integrated Allocation Scores (IAS) centered at 15,000.", digits = 0) |>
  print(include.rownames = FALSE, )
@

>>>>

The integrated allocation score (IAS) summarizes allocation scores (AS) across a range of possible values of the constraint ($K$), possibly taking weights into account for different values of $K$ that might be more or less likely (Section \ref{sec:methods.detailed.integrated_allocation}).
This could be useful in situations where the actual constraint may not be known, or could only be specified as a probability distribution.
Unlike in the above analyses where we conducted analyses assuming that $K$ was known to be 15,000, the analyses in this subsection are conducted assuming different distributions of $K$.

@@

AS was computed for a range of $K$ from 200 to 60,000 for forecasts made on 2020-12-20 predicting levels of hospitalizations on 2021-01-03 (Figure \ref{fig:multi-k}A).
These calculations highlight that AS was highest at the $K$ nearest to the observed value of \Sexpr{format(tot_y, big.mark = ",")}.
Rankings of AS from all models were fairly stable across a range of values for K, with some crossings, especially at $K$ values further away from the observed value.

IAS was computed for two distributions of $K$, one uniform across the entire range and the other a symmetric distribution around 15,000 (Figure \ref{fig:multi-k}B).
Both versions of the IAS were correlated with the original AS conducted at $K=15,000$, with the higher correlation coming from the distribution that was centered at $K=15,000$ (Figure \ref{fig:multi-k}C).
Model rankings based on the AC and the centered IAS were roughly similar, with the top and bottom two models being the same for both scores (Table \ref{tab:multi-k-scores}).

@@

<<multi-k-scores, results='asis'>>=
left_join(ias, as) |>
  rename(`IAS centered at 15k` = IAS_wt,
         `IAS uniform` = IAS) |>
  arrange(-`IAS centered at 15k`) |>
  xtable::xtable(caption = "Allocation scores shown in Figure \\ref{fig:multi-k}C, sorted by Integrated Allocation Scores (IAS) centered at 15,000.",
                 digits = 0,
                 label = "tab:multi-k-scores") |>
  print(include.rownames = FALSE, )
@
